---
title: "ANLY 506 Final Report"
author: "Cemin Sunny (192524)"
date: "April 24, 2019"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr);library(ggplot2)
BikeData <- read.csv("D:/R Working Directory/bikeVendors.csv", header=TRUE, sep=",")
```

### Some of the question this analysis will help to answer
#### What are the types of bikes in this data?
#### What are these bikes used for?
#### How each type of bike used for? 
#### What is the price range for these bikes?
#### What type of frames do these bikes have?
#### Do the frames have a correlation with price? 


```

## Data Exploration.
###Two types of Bikes are Mountain and Road.
```{r warning=FALSE, message=FALSE}

plot(BikeData$category1)
```

#### These bikes are used for Trail, Elite Road, Sport, Cross Country race, Fat Bike, Trail, Over Mountain, Triathalon, Cyclocross,and Endurance Road.
```{r warning=FALSE, message=FALSE}
plot(BikeData$category2)
```

#### Road bikes are used for Elite Road, Triathalon, Cyclocross,and Endurance Road.
```{r warning=FALSE, message=FALSE}
CTRoad <- filter(BikeData, category1 == "Road")
plot(CTRoad$category2)
```

#### Mountain bikes are used for Trail, Sport, Cross Country Race, Fat Bike, Cross Country Race, Sport,and Over Mountain. 
```{r warning=FALSE, message=FALSE}
CTMountain <- filter(BikeData, category1 == "Mountain")
plot(CTMountain$category2)
```

## Data Analysis.
### Expensive and economical bikes.
####Bikes that are priced over $5000 has been categorized as expensive and below $5000 as economical.Expensive and economical has both mountain and road bikes.
```{r warning=FALSE, message=FALSE}
Expensive <- filter(BikeData, price >= 5000)

Economical <- filter(BikeData, price <= 5000)
```

#### Most of the expensive bikes are made of carbon frame.

```{r warning=FALSE, message=FALSE}
plot(Expensive$frame)
```

#### Most of the aluminum frame bikes are economical.
```{r warning=FALSE, message=FALSE}
Aluminumframe <- filter(BikeData, frame == "Aluminum")
plot(Aluminumframe$price)
````

#### However,economical bikes does have both aluminum and carbon frame bikes.Not all carbon frame bikes are expensive.

```{r warning=FALSE, message=FALSE}

plot(Economical$frame)
Carbonframe <- filter(BikeData, frame == "Carbon")

plot(Carbonframe$price)

```

### Triathalon bikes.
#### Triathalon bikes are not expensive.However, all triathalon bikes are made of carbon.   
```{r warning=FALSE, message=FALSE}
Triathalon <- filter(BikeData, category2 == "Triathalon")
```{r warning=FALSE, message=FALSE}
plot(Triathalon$price)
plot(Triathalon$frame)
```

### Endurance Road Bikes.
#### Endurance road bikes has both carbon and aluminum frame, 
```{r warning=FALSE, message=FALSE}
EnduranceRoadBike <- filter(BikeData, category2 == "Endurance Road")

plot(EnduranceRoadBike$frame)
```

